Addendum to a survey of HTTP caching on the Semantic Web

### 2015-03-20 sanity/report.tex
Proofreading
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1108 43ef1190-90fd-4dd7-a769-d0121f02b80e

In this addendum, we document in detail several aspects that there
were not sufficient space for in the conference paper. Since we made
the assumption that the relevant headers are mostly the same for each
host, Section~\ref{app:reduction} documents how the large BTC2014 data
set is reduced to visit a large number hosts, but a small number of
resources. Then, Section~\ref{app:fetcher} discusses the system we
developed to visit these resources and extract the information that we
were interested. Section~\ref{app:stats} documents our main
statistical method and Section~\ref{app:qqplot} has an analysis of
valid versus invalid responses.

@@

The parallel spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URLs found by previous steps for
that host. Since the BTC2014 recorded the \httph{Expires},
\httph{Last-Modified} and \httph{ETag} headers where they existed, we
first examined if any of the resources were still fresh, but none
were. Wherever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

@@

The hypothesis tests in this paper is implemented using \emph{contingency
  tables} (see e.g. \cite{kn:bj}). This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

>>>>

In this addendum, we document in detail several aspects that there
were not sufficient space for in the conference paper. Since we made
the assumption that the relevant headers are mostly the same for each
host, Section~\ref{app:reduction} documents how the large BTC2014 data
set is reduced to visit a large number hosts, but a small number of
resources. Then, Section~\ref{app:fetcher} discusses the system we
developed to visit these resources and extract the information that we
were interested. Section~\ref{app:stats} documents our main
statistical method and Section~\ref{app:qqplot} has an analysis of
the distribution of valid versus invalid responses.

@@

The parallel spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URLs found by previous steps for
that host. Since the BTC2014 recorded the \httph{Expires},
\httph{Last-Modified} and \httph{ETag} headers where they existed, we
first examined whether any of the resources were still fresh, but none
were. Wherever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

@@

The hypothesis tests in this paper were implemented using \emph{contingency
  tables} (see e.g. \cite{kn:bj}). This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.
